### 2017-12-11 submission/manuscript.Rmd
add intro update -- more explicit differences

>>>>

In comparison to the previous meta-analysis, this study  significantly increases the total stool samples investigated, examines differences between stool and tissue microbiota in the context of CRC, and takes a more community centric approach rather than a biomarker focused approach to investigating commonalities across study for the microbiota and CRC severity. Importantly, this community centric approach could provide valuable insights into the importance of accounting for the community in CRC disease not previously provided by earlier meta-analysis studies [@shah_leveraging_2017].

### 2017-12-11 submission/manuscript.tex
add intro update -- more explicit differences

>>>>

In comparison to the previous meta-analysis, this study significantly
increases the total stool samples investigated, examines differences
between stool and tissue microbiota in the context of CRC, and takes a
more community centric approach rather than a biomarker focused approach
to investigating commonalities across study for the microbiota and CRC
severity. Importantly, this community centric approach could provide
valuable insights into the importance of accounting for the community in
CRC disease not previously provided by earlier meta-analysis studies
{[}11{]}.
